IML Term project

### 2022-12-07 main_markdown.rmd
.

# loocv
for(i in 1:dim(npf)[1]){
  mod <- lda(class2 ~ ., npf[split != i, ])
  lda.pred.loocv[split == i] <- predict(mod, npf[split == i, ])$posterior[,2]
  ## 168
  mod <- lda(class2 ~ ., npf.168[split != i, ])
  lda.pred.loocv.168[split == i] <- predict(mod, npf.168[split == i, ])$posterior[,2]
}

@@

# loocv
for(i in 1:dim(npf)[1]){
  mod <- lda(class2 ~ ., npf.pca[split != i, ])
  lda.pred.loocv.pca[split == i] <- predict(mod, npf.pca[split == i, ])$posterior[,2]
  ## 168
  mod <- lda(class2 ~ ., npf.168.pca[split != i, ])
  lda.pred.loocv.168.pca[split == i] <- predict(mod, npf.168.pca[split == i, ])$posterior[,2]
}

@@

# loocv
for(i in 1:dim(npf)[1]){
  mod <- qda(class2 ~ ., npf[split != i, ])
  qda.pred.loocv[split == i] <- predict(mod, npf[split == i, ])$posterior[,2]
  ## 168
  mod <- qda(class2 ~ ., npf.168[split != i, ])
  qda.pred.loocv.168[split == i] <- predict(mod, npf.168[split == i, ])$posterior[,2]
}

@@

# loocv
for(i in 1:dim(npf)[1]){
  mod <- qda(class2 ~ ., npf.pca[split != i, ])
  qda.pred.loocv.pca[split == i] <- predict(mod, npf.pca[split == i, ])$posterior[,2]
  ## 168
  mod <- qda(class2 ~ ., npf.168.pca[split != i, ])
  qda.pred.loocv.168.pca[split == i] <- predict(mod, npf.168.pca[split == i, ])$posterior[,2]
}

@@

# 168
qda_acc.168.pca <- data.frame(CV = accuracy(qda.pred.cv.168.pca, npf.168.pca$class2),
                              LOOCV = accuracy(qda.pred.loocv.168.pca, npf.168.pca$class2))
qda_perp.168.pca <- data.frame(CV = perplexity(qda.pred.cv.168.pca, npf.168.pca$class2),
                               LOOCV = perplexity(qda.pred.loocv.168.pca, npf.168.pca$class2))
kable(cbind(qda_acc.168.pca,
            qda_perp.168.pca)) %>%
  add_header_above(c("Accuracy" = 2, "Perplexity" = 2))%>%
  kable_styling(latex_options = "HOLD_position")
```

### GLM
```{r glm, warning=FALSE, fig.height=4}
mod1<-glm(class2~., npf, family=binomial(link="logit"))
mod2<-glm(class2~., npf, family=binomial(link="probit"))
plot(mod1)
prob1<-predict(mod1, npf, type="response")
pred1<-c()
perp1<-c()
for(i in 1:dim(npf)[1]){
  if(prob1[i]>=0.5){
    pred1<-c(pred1,1)
  } else{
    pred1<-c(pred1,0)
  }
  if(npf$class2[i]==1){
    perp1<-c(perp1,prob1[i])
  } else{
    perp1<-c(perp1,1-prob1[i])
  }
}
```

>>>>

# loocv
for(i in 1:dim(npf)[1]){
  mod <- lda(class2 ~ ., npf[-i, ])
  lda.pred.loocv[i] <- predict(mod, npf[i, ])$posterior[,2]
  ## 168
  mod <- lda(class2 ~ ., npf.168[-i, ])
  lda.pred.loocv.168[i] <- predict(mod, npf.168[i, ])$posterior[,2]
}

@@

# loocv
for(i in 1:dim(npf)[1]){
  mod <- lda(class2 ~ ., npf.pca[-i, ])
  lda.pred.loocv.pca[i] <- predict(mod, npf.pca[i, ])$posterior[,2]
  ## 168
  mod <- lda(class2 ~ ., npf.168.pca[-i, ])
  lda.pred.loocv.168.pca[i] <- predict(mod, npf.168.pca[i, ])$posterior[,2]
}

@@

# loocv
for(i in 1:dim(npf)[1]){
  mod <- qda(class2 ~ ., npf[-i, ])
  qda.pred.loocv[i] <- predict(mod, npf[i, ])$posterior[,2]
  ## 168
  mod <- qda(class2 ~ ., npf.168[-i, ])
  qda.pred.loocv.168[i] <- predict(mod, npf.168[i, ])$posterior[,2]
}

@@

# loocv
for(i in 1:dim(npf)[1]){
  mod <- qda(class2 ~ ., npf.pca[-i, ])
  qda.pred.loocv.pca[i] <- predict(mod, npf.pca[i, ])$posterior[,2]
  ## 168
  mod <- qda(class2 ~ ., npf.168.pca[-i, ])
  qda.pred.loocv.168.pca[i] <- predict(mod, npf.168.pca[i, ])$posterior[,2]
}

@@

# 168
qda_acc.168.pca <- data.frame(CV = accuracy(qda.pred.cv.168.pca, npf.168.pca$class2),
                              LOOCV = accuracy(qda.pred.loocv.168.pca, npf.168.pca$class2))
qda_perp.168.pca <- data.frame(CV = perplexity(qda.pred.cv.168.pca, npf.168.pca$class2),
                               LOOCV = perplexity(qda.pred.loocv.168.pca, npf.168.pca$class2))
kable(cbind(qda_acc.168.pca,
            qda_perp.168.pca)) %>%
  add_header_above(c("Accuracy" = 2, "Perplexity" = 2))%>%
  kable_styling(latex_options = "HOLD_position")
```
## Multiple classes

### Naive Bayes on the npf-dataset

```{r naive bayes multiclass, warning=FALSE, fig.height=4}

# Use class4 instead of class2
npf.class4 <- npf[,1:100]
npf.class4$class4 <- npfOrig$class4

multinb.pred.loocv <- rep(0,nrow(npf.class4))

# loocv
for(i in 1:dim(npf.class4)[1]){
  mod <- naiveBayes(class4 ~ ., npf.class4[-i, ])
  multinb.pred.loocv[i] <- predict(mod, npf.class4[i, ])
}

multinb.pred.loocv[multinb.pred.loocv == 1] <- "Ia"
multinb.pred.loocv[multinb.pred.loocv == 2] <- "Ib"
multinb.pred.loocv[multinb.pred.loocv == 3] <- "II"
multinb.pred.loocv[multinb.pred.loocv == 4] <- "nonevent"

mean(as.numeric(multinb.pred.loocv == npf.class4$class4))
```
### LDA on the npf.168-dataset

```{r lda multiclass, warning=FALSE, fig.height=4}

# Use class4 instead of class2
npf.168.class4 <- npf.168[,1:36]
npf.168.class4$class4 <- npfOrig$class4

multilda.pred.loocv <- rep(0,nrow(npf.168.class4))

# loocv
for(i in 1:dim(npf.168.class4)[1]){
  mod <- lda(class4 ~ ., npf.168.class4[-i, ])
  multilda.pred.loocv[i] <- predict(mod, npf.168.class4[i, ])$class
}

multilda.pred.loocv[multilda.pred.loocv == 1] <- "Ia"
multilda.pred.loocv[multilda.pred.loocv == 2] <- "Ib"
multilda.pred.loocv[multilda.pred.loocv == 3] <- "II"
multilda.pred.loocv[multilda.pred.loocv == 4] <- "nonevent"

mean(as.numeric(multilda.pred.loocv == npf.168.class4$class4))
```

### QDA on the npf.pca-dataset

```{r qda multiclass, warning=FALSE, fig.height=4}

# Use class4 instead of class2
npf.pca.class4 <- npf.pca[,1:12]
npf.pca.class4$class4 <- npfOrig$class4

multiqda.pred.loocv <- rep(0,nrow(npf.pca.class4))

# loocv
for(i in 1:dim(npf.pca.class4)[1]){
  mod <- qda(class4 ~ ., npf.pca.class4[-i, ])
  multiqda.pred.loocv[i] <- predict(mod, npf.pca.class4[i, ])$class
}

multiqda.pred.loocv[multiqda.pred.loocv == 1] <- "Ia"
multiqda.pred.loocv[multiqda.pred.loocv == 2] <- "Ib"
multiqda.pred.loocv[multiqda.pred.loocv == 3] <- "II"
multiqda.pred.loocv[multiqda.pred.loocv == 4] <- "nonevent"

mean(as.numeric(multiqda.pred.loocv == npf.pca.class4$class4))
```

### QDA on the npf.168.pca-dataset

```{r qda multiclass 168, warning=FALSE, fig.height=4}

# Use class4 instead of class2
npf.168.pca.class4 <- npf.168.pca[,1:12]
npf.168.pca.class4$class4 <- npfOrig$class4

multiqda.pred.loocv <- rep(0,nrow(npf.168.pca.class4))

# loocv
for(i in 1:dim(npf.168.pca.class4)[1]){
  mod <- qda(class4 ~ ., npf.168.pca.class4[-i, ])
  multiqda.pred.loocv[i] <- predict(mod, npf.168.pca.class4[i, ])$class
}

multiqda.pred.loocv[multiqda.pred.loocv == 1] <- "Ia"
multiqda.pred.loocv[multiqda.pred.loocv == 2] <- "Ib"
multiqda.pred.loocv[multiqda.pred.loocv == 3] <- "II"
multiqda.pred.loocv[multiqda.pred.loocv == 4] <- "nonevent"

mean(as.numeric(multiqda.pred.loocv == npf.168.pca.class4$class4))
```
### GLM
```{r glm, warning=FALSE, fig.height=4}
mod1<-glm(class2~., npf, family=binomial(link="logit"))
mod2<-glm(class2~., npf, family=binomial(link="probit"))
plot(mod1)
prob1<-predict(mod1, npf, type="response")
pred1<-c()
perp1<-c()
for(i in 1:dim(npf)[1]){
  if(prob1[i]>=0.5){
    pred1<-c(pred1,1)
  } else{
    pred1<-c(pred1,0)
  }
  if(npf$class2[i]==1){
    perp1<-c(perp1,prob1[i])
  } else{
    perp1<-c(perp1,1-prob1[i])
  }
}
```
